\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Luca Coccia} \\ \vspace{1pt}
    Palestrina, Italy \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\href{mailto:lucaccc01@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{lucaccc01@gmail.com}} ~ 
    \href{https://github.com/lucaccc1}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/lucaccc1}}
    \vspace{-8pt}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sapienza Università di Roma}{Sep 2023 -- Expected Oct 2026}
      {Bachelor of Science in Computer Engineering}{Rome, Italy}
      \resumeItemListStart
        \resumeItem{\textbf{Thesis:} Evaluation of LLMs for the automatic description of functions during static analysis of stripped binaries.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Relevant Coursework}
    \begin{multicols}{3}
        \begin{itemize}[itemsep=-5pt, parsep=3pt]
            \item\small Software Engineering
            \item Operating Systems
            \item AI Fundamentals
            \item Web Technologies
            \item Algorithms
            \item Data Structures
        \end{itemize}
    \end{multicols}
    \vspace*{2.0\multicolsep}

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sapienza Università di Roma}{Mar 2026 -- Jun 2026}
      {Undergraduate Research Intern}{Rome, Italy}
      \resumeItemListStart
        \resumeItem{Conducted academic research on AI-assisted reverse engineering, independently defining the project scope and methodology under faculty supervision.}
        \resumeItem{Designed comprehensive evaluation frameworks and custom quantitative metrics to assess LLM reasoning capabilities on assembly code.}
      \resumeItemListEnd

    \resumeSubheading
      {Servizio Civile Universale}{Jul 2024 -- Jul 2025}
      {Volunteer}{Palestrina, Italy}
      \resumeItemListStart
        \resumeItem{Supported local community projects, demonstrating strong teamwork, communication, and organizational skills.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/lucaccc1/valutazione-llm-per-analisi-statica-binari}{LLM Evaluation for Static Analysis Tool}} $|$ \emph{Python, IDA Pro, Bash}}{Mar 2026 -- Jun 2026}
          \resumeItemListStart
            \resumeItem{Engineered a headless tool to automatically assign descriptive names to functions in stripped binaries, cutting down the bottleneck in static analysis.}
            \resumeItem{Developed a custom technical bridge between IDA Pro and Python to extract binary data and seamlessly interface with Large Language Models.}
            \resumeItem{Evaluated the performance and accuracy of various LLMs in understanding and summarizing assembly-level code.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{\href{https://github.com/lucaccc1/rinnemon}{Rinnemon}} $|$ \emph{React, Node.js, JavaScript, HTML/CSS}}{Mar 2026 -- Present}
          \resumeItemListStart
            \resumeItem{Designed and developed a fully playable roguelike web game inspired by Pokémon mechanics, optimized specifically for PC browser experiences.}
            \resumeItem{Implemented interactive front-end mechanics and game state logic utilizing modern React hooks and Node.js.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C, Java, JavaScript, HTML/CSS} \\
     \textbf{Frameworks \& Libraries}{: React, Node.js, Pandas} \\
     \textbf{Developer Tools}{: Git, Linux, IDA Pro, LaTeX} \\
     \textbf{Databases}{: PostgreSQL} \\
     \textbf{Spoken Languages}{: Italian (Native), English (B2)}
    }}
 \end{itemize}
 \vspace{-16pt}

\section{Leadership \& Teaching}
    \resumeSubHeadingListStart
        \resumeSubheading{Freelance STEM Tutor}{2023 -- Present}{Private Tutor}{Palestrina, Italy}
            \resumeItemListStart
                \resumeItem{Mentored high school and university students in STEM subjects (Mathematics, Computer Science, Physics).}
                \resumeItem{Simplified complex technical concepts into accessible lessons, improving students' problem-solving skills and academic performance.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


\end{document}
